---
title: ECORAP analysis template 
author: "ECO Rapper"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format: 
  html:
    css: resources/AIMS-style.css
    toc: true
    toc-float: true
    number-sections: true
    number-depth: 3
    embed-resources: true
    code-fold: false
    code-tools: true
    code-summary: "Show the code"
crossref:
  fig-title: '**Figure**'
  fig-labels: arabic
  tbl-title: '**Table**'
  tbl-labels: arabic
engine: knitr
bibliography: resources/references.bib
output_dir: "docs"
---

```{r chunks, results='markdown', eval=TRUE, echo = FALSE}
knitr::read_chunk('../R/functions.R')
knitr::read_chunk('../R/analysis.R')
```

# Preparations

- Load any helper functions

```{r loadFunctions, results='markdown', eval=FALSE}
```

```{r setup, include=FALSE, warnings=FALSE, message=FALSE}
```

- Load required packages
```{r loadPackages, results='markdown', eval = TRUE, warnings = FALSE, message = FALSE}
```

- Prepare paths
```{r preparePaths, results='markdown', eval = TRUE}
```

# Coral Growth

## Load Data

1. Load the data
```{r CoralGrowth readData, results='markdown', eval=TRUE}
```
2. Glimpse the data

```{r CoralGrowth glimpse, results='markdown', eval=TRUE}
```

## Data processing

1. Replace Acyt and Ahya with Atab in all Class* fields
2. Exclude colonies that were dead or missing in 2022
3. Only keep colonies that have good images in 2021 and 2022
4. Drop the extraneous columns
5. Add a colony ID
6. Pivote longer
7. ~~Express area in cm2~~
8. Define unique hierarchical levels
9. Define Site_code as each unique Reef/Site/Zone combination
 


# Fish Abundance
